Methods for Large Scale Learning to Rank

### 2014-04-06 report/Chapters/CrossBenchmarkComparison.tex
LETOR 2.0 metingen IPRank gevonden + begin overzicht unusable papers

AdaRank-\acs{nDCG} &  & \cite{Busa-Fekete2013,Tan2013} & List\acs{MLE} &  & \cite{Lin2010, Gao2014} \\ 

@@

\acs{GP}Rank &  & \cite{Torkestani2012} & REG-SHF-SDCG & \cite{Wu2009} & \cite{Wu2009} \\ 

@@

Group\acs{MLE} &  &  & SmoothGrad &  & \cite{Tan2013} \\ 

@@

\acs{IP}Rank &  & \cite{Torkestani2012} & SoftRank &  & \cite{Qin2010b} \\ 

@@

Kernel-\acs{PCA} &  &  & SparseRank & \cite{Lai2013b} & \cite{Lai2013b} \\ 

>>>>

AdaRank-\acs{nDCG} &  & \cite{Busa-Fekete2013,Tan2013} & List\acs{MLE} &  & \cite{Lin2010, Lin2011, Gao2014} \\ 

@@

\acs{GP}Rank & \cite{Silva2009} & \cite{Torkestani2012} & REG-SHF-SDCG & \cite{Wu2009} & \cite{Wu2009} \\ 

@@

Group\acs{MLE} & \cite{Lin2010} & \cite{Lin2011} & SmoothGrad &  & \cite{Tan2013} \\ 

@@

\acs{IP}Rank & \cite{Wang2009b} & \cite{Torkestani2012} & SoftRank &  & \cite{Qin2010b} \\ 

@@

Kernel-\acs{PCA} RankBoost & \cite{Duh2008} & \cite{Duh2008} & SparseRank & \cite{Lai2013b} & \cite{Lai2013b} \\ 
